working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-02-22 Manuscript_draft/Manuscript_draft.Rmd
methods changes

Foreign pollen effect was studied through two different treatments, one with 50% conspecific pollen and 50% heterospecific pollen and a second one with 100% foreign pollen (N=10) [this second I don't get, maybe explain it's ultility.](). Therefore, 180 different combinations were performed with N=10 per combination. Seed set was the proxy of effect for all our treatments. Moreover, hand cross pollination (between individuals of the same species), hand self pollination, apomixis (bagged emasculated flowers) and natural selfing were tested for each species (N=10). For the treatments with foreign pollen and hand cross pollination, flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick. Hand-pollination was conducted with 3-4 gentle touches on the stigma surface. [The mixes of pollen were realized on an eppendorf based on the pollen counts made with Neubaeur chamber (each anther was counted 4 times for 20 different anthers per species)-IB explain better and give a bit more of detail](). In order to confirm that the treatments applied were 50-50 percent pollen, for each focal species the total stigmatic load of pollen was counted from one donor of each family (N=3).

>>>>

Foreign pollen effect was studied through two different treatments, one with 50% conspecific pollen and 50% heterospecific pollen and a second one with 100% foreign pollen (N=10) in order to see if foreign pollen can trigger fruit production by itself or even seeds through ovule usurpation. Therefore, 180 different combinations were performed with N=10 per combination. Seed set was the proxy of effect for all our treatments. Moreover, hand cross pollination (between individuals of the same species), hand self pollination, apomixis (bagged emasculated flowers) and natural selfing were tested for each species (N=10). For the treatments with foreign pollen and hand cross pollination, flowers were emasculated the day prior anthesis and hand pollinated next day with a toothpick. Hand-pollination was conducted with 3-4 gentle touches on the stigma surface. For each species 20 anthers were collected and their pollen counted with a hemocytometer, each anther was counted 4 times and then an average of these counts was performed. Once, the average number of pollen grains per anther was known, the proportion of anthers per mix was calculated in order to achieve a 50-50% mix.  In order to confirm that the treatments applied were the desire proportions, for each focal species the total stigmatic load of pollen was counted from one donor of each family (N=3).

### 2019-02-22 Manuscript_draft/Manuscript_draft.tex
methods changes

Foreign pollen effect was studied through two different treatments, one
with 50\% conspecific pollen and 50\% heterospecific pollen and a second
one with 100\% foreign pollen (N=10) \href{}{this second I don't get,
maybe explain it's ultility.}. Therefore, 180 different combinations
were performed with N=10 per combination. Seed set was the proxy of
effect for all our treatments. Moreover, hand cross pollination (between
individuals of the same species), hand self pollination, apomixis
(bagged emasculated flowers) and natural selfing were tested for each
species (N=10). For the treatments with foreign pollen and hand cross
pollination, flowers were emasculated the day prior anthesis and hand
pollinated next day with a toothpick. Hand-pollination was conducted
with 3-4 gentle touches on the stigma surface. \href{}{The mixes of
pollen were realized on an eppendorf based on the pollen counts made
with Neubaeur chamber (each anther was counted 4 times for 20 different
anthers per species)-IB explain better and give a bit more of detail}.
In order to confirm that the treatments applied were 50-50 percent
pollen, for each focal species the total stigmatic load of pollen was
counted from one donor of each family (N=3).

>>>>

Foreign pollen effect was studied through two different treatments, one
with 50\% conspecific pollen and 50\% heterospecific pollen and a second
one with 100\% foreign pollen (N=10) in order to see if foreign pollen
can trigger fruit production by itself or even seeds through ovule
usurpation. Therefore, 180 different combinations were performed with
N=10 per combination. Seed set was the proxy of effect for all our
treatments. Moreover, hand cross pollination (between individuals of the
same species), hand self pollination, apomixis (bagged emasculated
flowers) and natural selfing were tested for each species (N=10). For
the treatments with foreign pollen and hand cross pollination, flowers
were emasculated the day prior anthesis and hand pollinated next day
with a toothpick. Hand-pollination was conducted with 3-4 gentle touches
on the stigma surface. For each species 20 anthers were collected and
their pollen counted with a hemocytometer, each anther was counted 4
times and then an average of these counts was performed. Once, the
average number of pollen grains per anther was known, the proportion of
anthers per mix was calculated in order to achieve a 50-50\% mix. In
order to confirm that the treatments applied were the desire
proportions, for each focal species the total stigmatic load of pollen
was counted from one donor of each family (N=3).
